greta.Rmd

### 2019-07-12 notebook/ghost-fit.Rmd
notes

```{r}
samples <-  
  map_dfr(draws, 
          function(x) data.frame(x, t = 1:dim(x)[1]), 
          .id = "chain") %>% 
  gather(variable, value, -t, -chain)

samples %>%  
  ggplot(aes(t,value, col=chain, group=chain)) + 
  geom_line() +
  facet_wrap(~variable, scales = "free") + 
  scale_color_viridis_d()
```

>>>>

```{r}
samples <-  
  map_dfr(draws, 
          function(x) data.frame(x, t = 1:dim(x)[1]), 
          .id = "chain") %>% 
  gather(variable, value, -t, -chain)
```

```{r include=FALSE}
## manual version of bayesplot::mcmc_trace()
samples %>%  
  ggplot(aes(t,value, col=chain, group=chain)) + 
  geom_line() +
  facet_wrap(~variable, scales = "free") + 
  scale_color_viridis_d()
```
